Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-11-26 manuscript.qmd
fix some citations

This paper builds on the previously developed unilateral model for ipsilateral lymph node involvement presented in [@ludwig_modelling_2024]. Below, we briefly recap the unilateral model to introduce the notation required for extending the framework to a bilateral model, described in @sec-ext-to-contra. For further details on the ipsilateral model, refer to earlier publications [@ludwig_hidden_2021; @ludwig_modelling_2024].

@@

Oropharyngeal tumors occur in distinct subsites, such as the base of the tongue or the tonsils, which may exhibit slightly different lymphatic metastatic patterns. Incorporating subsite-specific information into the model could enhance its predictive accuracy. Preliminary investigations suggest that a mixture model may effectively capture these subsite-specific spread patterns [@_proceedings_2024; @zora231470].

>>>>

This paper builds on the previously developed unilateral model for ipsilateral lymph node involvement presented in [@ludwig_modelling_2024]. Below, we briefly recap the unilateral model to introduce the notation required for extending the framework to a bilateral model, described in @sec-ext-to-contra. For further details on the ipsilateral model, refer to earlier publications [@ludwig_hidden_2021;@ludwig_modelling_2024].

@@

Oropharyngeal tumors occur in distinct subsites, such as the base of the tongue or the tonsils, which may exhibit slightly different lymphatic metastatic patterns. Incorporating subsite-specific information into the model could enhance its predictive accuracy. Preliminary investigations suggest that a mixture model may effectively capture these subsite-specific spread patterns [@sarrut_proceedings_2024;@ludwig_modelling_2023a].
